---
title: "HOPETemplate"
author: "Place"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: kable
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,     # don't show code chunks
  message = FALSE,  # don't show code messages
  warning = FALSE,  # don't show code warnings
  out.width = "75%" # show images at 75% page width
)
library(markr)
```

```{r, eval=F}
# set eval=T to knit this example for debugging
ma#rks <- demo_marks  # load your data as marks
# convert the marks column to letter grades

name <- marks[1, ]    # selects just the first row
```

### `r name$name`  

## General Information

This is a summarized report of the information obtained from your Certified Community Behavioral Health Clinic (CCBHC)  National Outcome Measures interview, which occurred on 2-5-2022.

## Behavioral Health Diagnoses

These are the diagnoses we submitted to SAMHSA as they are stated in your Treatment Plan at institution:

Primary: `r name$dx1`

Secondary: `r name$dx2`

Tertiary: `r name$dx3`


## Individual Feedback

`r name$comments`